---
title: "Social Survey 2010"
author: "Put your name here!"
date: "Fall 2018"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyvertse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

Use the data from the 2010 general social survey to explore whether belief in continental drift (condrift), views on capitol punishment (cappun), and race (race) are independent of each other.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
alldata <- read.csv(file="gss2010.csv", header=TRUE)
#names(alldata)
```


## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
barchartGC(~race+condrift, data=alldata, type = "percent") 
```

There seems to be a difference between the way black people percieve continental drift from the white people and other's races due to the results from the barcharts. The number of black people that believe continental drift to be false is twice that of the number of whites and other races say it is false.  

```{r}
barchartGC(~race+cappun, data=alldata, type = "percent") 
```
  
Based on the results more black people are opposed to capital punishment, where as the other races and whites and more in favor to capital punishment with a majority of whites haveing a higher percent of favoring then opposing punishment.  

```{r}
barchartGC(~condrift+cappun, data=alldata, type = "percent") 
```
  
text entry here  

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
tab1 =xtabs(~race+condrift, data=alldata)
rowPerc(tab1)
colPerc(tab1)
```
What we see is that there is very little difference between the way whites and other races and how they percieve continental drift compared to black people, where 23% of them believe it to be false compared to whties and others only 8 and 9 percent respectivley.  

```{r}
tab2 =xtabs(~race+cappun, data=alldata)
rowPerc(tab2)
colPerc(tab2)
```
  
text here  

```{r}
tab3 =xtabs(~condrift+cappun, data=alldata)
rowPerc(tab3)
colPerc(tab3)
```
  
text entry here  

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisqtestGC(tab1,graph = TRUE)
```
  
DUe to the low value of the P-value we will reject the null hyptohesis.Based on the test we can comme to the conclusion that these two variables are independent due to the low P-value.  

```{r}
chisqtestGC(tab2,graph = TRUE)
```
  
text entry here  

```{r}
chisqtestGC(tab3,graph = TRUE)
```
  
text here  

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
